% =========================================================
% daftarpustaka.tex - DAFTAR PUSTAKA
% =========================================================

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{DAFTAR PUSTAKA}
\renewcommand\bibname{DAFTAR PUSTAKA}

\begin{thebibliography}{99}

\bibitem{worldbankFPV2019}
World Bank Group, ESMAP, and SERIS, \textit{Where Sun Meets Water: Floating Solar Handbook for Practitioners}. Washington, DC, USA: World Bank, 2019. [Online]. Available: \url{https://openknowledge.worldbank.org/entities/publication/645af5c2-9fbc-5575-8fd5-6dbed04e09b4}

\bibitem{ieaFPV2025}
IEA PVPS Task 13, \textit{Floating Photovoltaic Power Plants: A Review of Energy Yield, System Reliability and Operations and Maintenance}. International Energy Agency Photovoltaic Power Systems Programme, 2025. [Online]. Available: \url{https://iea-pvps.org/key-topics/t13-floating-pv-plants-review-2025/}

\bibitem{ketjoy2022}
N. Ketjoy, P. Mensin, and W. Chamsa-ard, ``Impacts on Insulation Resistance of Thin Film Modules: A Case Study of a Flooding of a Photovoltaic Power Plant in Thailand,'' \textit{PLOS ONE}, vol. 17, no. 9, p. e0274839, 2022.

\bibitem{linwu2025}
J.-H. Lin and Y.-K. Wu, ``Simulation and Fault Diagnosis Using Current-Voltage Characteristics of Photovoltaic Systems---A Case Study,'' in \textit{Engineering Proceedings}, vol. 92, no. 1. MDPI, 2025, p. 79.

\bibitem{pei2019}
T. Pei and X. Hao, ``A Fault Detection Method for Photovoltaic Systems Based on Voltage and Current Observation and Evaluation,'' \textit{Energies}, vol. 12, no. 9, p. 1712, 2019.

\bibitem{sugirianta2022}
I. B. K. Sugirianta, I. G. N. A. D. Saputra, I. M. Purbhawa, I. G. K. S. Budarsa, and I. K. Ta, ``Short and Open Circuit Fault Detection in On-Grid Photovoltaic Systems 1MWp Bangli Based on Current and Voltage Observation,'' \textit{Journal of Computer Science and Technology Studies}, vol. 4, no. 2, pp. 105--117, 2022.

\bibitem{nunes2022}
H. G. G. Nunes et al., ``Bypass Diode Effect and Photovoltaic Parameter Estimation under Partial Shading Using a Hill Climbing Neural Network Algorithm,'' \textit{Frontiers in Energy Research}, vol. 10, p. 837540, 2022.

\bibitem{pveducationBypass}
PV Education, ``Bypass Diodes,'' Online, 2024. [Online]. Available: \url{https://www.pveducation.org/pvcdrom/modules-and-arrays/bypass-diodes}

\bibitem{smaGroundFault}
SMA Solar Technology AG, ``Checking the PV System for Ground Faults,'' Online manual, 2024. [Online]. Available: \url{https://manuals.sma.de/SBxx-1VL-40/en-US/391466379.html}

\bibitem{villalva2009}
M. G. Villalva, J. R. Gazoli, and E. R. Filho, ``Comprehensive Approach to Modeling and Simulation of Photovoltaic Arrays,'' \textit{IEEE Transactions on Power Electronics}, vol. 24, no. 5, pp. 1198--1208, 2009.

\bibitem{jinko2022}
JinkoSolar, \textit{Tiger Neo N-type 72HL4-BDV 560--580 Watt Bifacial Module with Dual Glass}. JinkoSolar Co., Ltd., 2022.

\bibitem{iec61215}
IEC, \textit{IEC 61215-1: Terrestrial Photovoltaic (PV) Modules---Design Qualification and Type Approval---Part 1: Test Requirements}. International Electrotechnical Commission, 2021.

\bibitem{iec60891}
IEC, \textit{IEC 60891: Photovoltaic Devices---Procedures for Temperature and Irradiance Corrections to Measured I--V Characteristics}. International Electrotechnical Commission, 2021.

\bibitem{iec61829}
IEC, \textit{IEC 61829: Photovoltaic (PV) Array---On-site Measurement of Current-voltage Characteristics}. International Electrotechnical Commission, 2015.

\bibitem{htiv6002025}
HT Instruments, \textit{I-V600 Professional I-V Curve Tracer up to 1500V,
40ADC}, Rel. 2.01, 2025.

\bibitem{pmse2021}
PT Pembangkitan Jawa Bali Masdar Solar Energi (PT PMSE), \textit{Profil Perusahaan dan Proyek PLTS Terapung Cirata 145 MWac}. Jakarta, Indonesia: PT PMSE, 2021. [Online]. Available: \url{https://pmse.solar/}

\end{thebibliography}